Large-scale harmonic patterns clustering

### 2010-03-21 Paper/Paper.tex
improved

\begin{figure}[htb]
  \centering
  \subfloat[][\small{Metallica}]{\label{fig:metallica2}\includegraphics[width=0.4\columnwidth]{metallica_pattern}}                
  \subfloat[][\small{Tori Amos / Suzanne Vega}]{\label{fig:amosvega2}\includegraphics[width=0.4\columnwidth]{toriamos_suzannevega_pattern}}
  \caption{\small{Typical patterns for different artists.}}
  \label{fig:typicalpat}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
  \subfloat[][\small{Metallica}]{\label{fig:metallica2}\includegraphics[width=0.35\columnwidth]{metallica_pattern}}
  \hspace{5mm}                
  \subfloat[][\small{Tori Amos / Suzanne Vega}]{\label{fig:amosvega2}\includegraphics[width=0.35\columnwidth]{toriamos_suzannevega_pattern}}
  \caption{\small{Typical patterns for different artists.}}
  \label{fig:typicalpat}
\end{figure}
